---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sparseNumericHW6

<!-- badges: start -->
[![R-CMD-check](https://github.com/Neena05/sparseNumericHW6/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/Neena05/sparseNumericHW6/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

sparseNumericHW6 provides an S4 class sparse_numeric for representing sparse numeric vectors in a memory-efficient way.
The package supports:

- Conversion between dense R numeric vectors and sparse representation

- Arithmetic operations (+, -, *) on sparse vectors

- Dot product (sparse_crossprod)

- Euclidean norm (norm)

- Standardization (standardize)

- Plotting overlapping non-zero elements

- A validity system enforcing data consistency

This package is useful for teaching S4 object systems and sparse representation concepts.

## Installation

You can install the development version of sparseNumericHW6 like so:

```{r, eval=FALSE}
# install directly from local folder
install.packages("path/to/sparseNumericHW6", repos = NULL, type = "source")
```

```{r}
# remotes::install_github("yourusername/sparseNumericHW6")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example, eval=FALSE}
library(sparseNumericHW6)

# Create a dense numeric vector

x <- c(0, 3, 0, 5, 0)

# Convert to sparse_numeric

sx <- as(x, "sparse_numeric")
sx
```

Arithmetic operations on sparse vectors:
```{r, eval=FALSE}
y <- as(c(1, 0, 2, 0, 4), "sparse_numeric")

sx + y
sx - y
sx * y
```

Dot product:
```{r, eval=FALSE}
sparse_crossprod(sx, y)
```

Standardization:
```{r, eval=FALSE}
standardize(sx)
```

Plotting overlapping non-zero elements:
```{r, eval=FALSE}
plot(sx, y)
```


Why use README.Rmd?

- Using README.Rmd instead of plain README.md lets you:

- Include executable R code chunks

- Automatically generate output tables and plots

- Guarantee documentation always stays up-to-date

- Knit the file into a clean GitHub-ready Markdown README
